A comparative analysis of penalized linear mixed models in structured genetic data

### 2021-02-14 main.tex
3.8 Software subsection

%------------------------------%
\subsection{Software}
\label{sec:software}
\anna{More discussion of software. Add a small section? R-based Software for lasso, pc-lasso, ggmix, plmm, PLINK functions, KING, snpRelate. Remove other mentions of software in other places and put them here}

@@

Although cross-validation (CV) and information criterion-based methods are commonly used to select $\lambda$ values, in this context they have the potential to result in misleading comparisons. Because lasso, PC-lasso, and LMM-lasso use different likelihoods, an information-criterion-based approach such as BIC would not lend itself to comparable results across methods. Meanwhile, whether cross-validation is advisable or not in the presence of dependent samples is an open question \citep{roberts2017cross}. \anna{We include a more detailed discussion of methods of penalty parameter selection for penalized LMMs to section \ref{sec:discussion}.}

@@

@@

\citet{Rakitsch2012} parameterize their model in terms of the variance components $\sigmass$ and $\delta := \sigmaee / \sigmass$ as previously discussed, however, we have implemented the LMM-lasso-Rakitsch method using an equivalent but more interpretable parameterization in terms of $\eta$ and $\sigmaee$ in the \texttt{R} package, \texttt{penalizedLMM}, available on the author's github repository \url{https://github.com/areisett/penalizedLMM}.

>>>>

@@

Although cross-validation (CV) and information criterion-based methods are commonly used to select $\lambda$ values, in this context they have the potential to result in misleading comparisons. Because lasso, PC-lasso, and LMM-lasso use different likelihoods, an information-criterion-based approach such as BIC would not lend itself to comparable results across methods. Meanwhile, whether cross-validation is advisable or not in the presence of dependent samples is an open question \citep{roberts2017cross}. \anna{We include a more detailed discussion of tuning parameter selection methods for penalized LMMs in Section \ref{sec:discussion}.}

@@

%------------------------------%
\subsection{\anna{Software}}
%------------------------------%
\label{sec:software}

All analyses and simulations were performed using \texttt{R} version ???. The ordinary lasso and PC-lasso methods were implemented using \texttt{glmnet} \citep{glmnet}. As described previously, LMM-lasso-ggmix was implemented using \texttt{ggmix} \citep{bhatnagar2020simultaneous}. The LMM-lasso-Rakitsch method was implemented using the \texttt{R} package, \texttt{penalizedLMM}, available on the github repository \url{https://github.com/areisett/penalizedLMM}. Although \citet{Rakitsch2012} parameterize their model in terms of the variance components $\sigmass$ and $\delta := \sigmaee / \sigmass$, \texttt{penalizedLMM} implements the LMM-lasso-Rakitsch method using an equivalent but more interpretable parameterization in terms of $\eta$ and $\sigmaee$. \texttt{penalizedLMM} additionally implements the elastic net, and the nonconvex penalties, MCP and SCAD.

@@
